taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-09-24 paper/manuscript.Rmd
Create provider table.

Names may also have an ambiguous resolution *discussion about taxonomic concepts here*. The spirit of taxadb is not to automate steps that require expert knowledge, but provide access to multiple potential "taxonomic theories".

@@

>>>>

Names may also have an ambiguous resolution leading to resolution by a different provider than the one specified, either as an accepted name or a synonym. Mapping between providers represent a meaningful scientific statement requiring an understanding of the underlying taxonomic concepts of each provider. The spirit of taxadb is not to automate steps that require expert knowledge, but provide access to multiple potential "taxonomic theories".

@@

```{r cache = FALSE, echo = FALSE}
tibble(provider = c("Integrated Taxonomic Information System", 
                                 "National Center for Biological Information's Taxonomy database",
                                 "Catalogue of Life",
                                 "Global Biodiversity Information Facility Taxonomic Backbone",
                                 "FishBase",
                                 #"SeaLifeBase",
                                 "Wikidata", "Open Tree Taxonomy",
                                 "International Union for Conservation of Nature and Natural Resources"),
                    abbreviation = c("itis", "ncbi", "col", "gbif", "fb", #"slb",
                                     "wd", "ott", "iucn"),
                    total_identifiers = map(abbreviation, 
                                            ~taxa_tbl(.x) %>% 
                                              select(acceptedNameUsageID) %>% pull() %>% n_distinct() %>% unlist())
) %>% printtable()
